### 2014-04-29 paper.tex
Added more info into the planner.

% Intro to all the following sections ( basically a summary)
% IK ID QP

@@

The

@@

There is already research on all kind of algorithms, but for future years the problem will become more on how to put all of these pieces of work together under one platform.

>>>>

@@

\subsection{Finding Graspable Points}
One of the challenges to come is the ability to grasp arbitrary points on an object. Contrary to most research where the robot is fixed to a table, such as the ones found in a car factory, or the PR2, in which the robot is on wheels, Atlas has to take the center of mass into consideration, making most conventional planners almost impossible to work with.

@@

There is already research on all kind of algorithms, but for future years the problem will become more on how to put all of these pieces of work together under one platform, and allow the robot to autonomously perform operations on the world.

Boston Dynamics has giving news that the Atlas robot may change over time, and this provides further complications on how to adapt the current code to also take into account the additional changes without breaking the current features.
